%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This is a slightly modified template of the one built by
% Steven V. Miller. Information can be found here:
%  http://svmiller.com/blog/2016/02/svm-r-markdown-manuscript/
%
% I added the use of raggedright to the anonymous option
% because journals,  the ability to put all the footnotes
% in endnotes, and the ability to manually adjust
% the starting page from the YAML header.
%
% Here are the options that you can define in the YAML
% header.
%
% fontfamily - self-explanatory
% fontsize - self-explanatory (e.g. 10pt, 11pt)
% anonymous - true/false. If true, names will be supressed and the
%                       text will be double-spaced and ragged
%                       right. For submission. 
% endnotes - true/false. If true, the footnotes will be put in a
%                   section at the end just ahead of the references.  
% keywords - self-explanatory
% thanks - shows up as a footnote to the title on page 1
% abstract - self explanatory
% appendix - if true, tables and figures will have  in
%                   front
% appendixletter - The letter to append to tables and figures in
%                             appendix
% pagenumber - Put in a number here to get a starting page number
%                         besides 1. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[11pt,]{article}
\usepackage[left=1in,top=1in,right=1in,bottom=1in]{geometry}
\usepackage{amsmath}
\usepackage{float}
\usepackage{dcolumn}

\newcommand*{\authorfont}{\fontfamily{phv}\selectfont}
\usepackage[]{mathpazo}


  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}



\usepackage{abstract}
\renewcommand{\abstractname}{}    % clear the title
\renewcommand{\absnamepos}{empty} % originally center

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\renewenvironment{abstract}
 {{%
    \setlength{\leftmargin}{0mm}
    \setlength{\rightmargin}{\leftmargin}%
  }%
  \relax}
 {\endlist}

\makeatletter
\def\@maketitle{%
  \newpage
%  \null
%  \vskip 2em%
%  \begin{center}%
  \let \footnote \thanks
    {\fontsize{18}{20}\selectfont\raggedright  \setlength{\parindent}{0pt} \@title \par}%
}
%\fi
\makeatother




\setcounter{secnumdepth}{0}



\title{An Analysis of Themes in Online Pornography  }



\author{\Large Ben Dreon\vspace{0.05in} \newline\normalsize\emph{University of Oregon, Sociology}  }


\date{}

\usepackage{titlesec}

\titleformat*{\section}{\normalsize\bfseries}
\titleformat*{\subsection}{\normalsize\itshape}
\titleformat*{\subsubsection}{\normalsize\itshape}
\titleformat*{\paragraph}{\normalsize\itshape}
\titleformat*{\subparagraph}{\normalsize\itshape}


\usepackage{natbib}
\bibliographystyle{./resources/ajs.bst}


%\renewcommand{\refname}{References}
%\makeatletter
%\renewcommand\bibsection{
%    \section*{{\normalsize{\refname}}}%
%}%
%\makeatother

\newtheorem{hypothesis}{Hypothesis}
\usepackage{setspace}

\makeatletter
\@ifpackageloaded{hyperref}{}{%
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
}
\@ifpackageloaded{color}{
    \PassOptionsToPackage{usenames,dvipsnames}{color}
}{%
    \usepackage[usenames,dvipsnames]{color}
}
\makeatother
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={Ben Dreon (University of Oregon, Sociology)},
             pdfkeywords = {Porn, Pornography, Human Sexuality},  
            pdftitle={An Analysis of Themes in Online Pornography},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

\usepackage{endnotes}


\newlength{\normalparindent}
\setlength{\normalparindent}{\parindent}

%prettier captions for figures and tables
%I am making the text of figure captions smaller but not table captions
\usepackage[labelfont=bf,labelsep=period]{caption}
\captionsetup[figure]{font=footnotesize}

\begin{document}
	
% \pagenumbering{arabic}% resets `page` counter to 1 
%
\setcounter{page}{1}

% \maketitle

{% \usefont{T1}{pnc}{m}{n}
\setlength{\parindent}{0pt}
\thispagestyle{plain}
{\fontsize{18}{20}\selectfont\raggedright 
\maketitle  % title \par  

}

{
   \vskip 13.5pt\relax \normalsize\fontsize{11}{12} 
\textbf{\authorfont Ben Dreon} \hskip 15pt \emph{\small University of Oregon, Sociology}   

}

}







\begin{abstract}

    \hbox{\vrule height .2pt width 39.14pc}

    \vskip 8.5pt % \small 

\noindent This is a test abstract


\vskip 8.5pt \noindent \emph{Keywords}: Porn, Pornography, Human Sexuality \par

    \hbox{\vrule height .2pt width 39.14pc}



\end{abstract}


\vskip 6.5pt

\noindent  \section{Introduction}\label{introduction}

Pornography is becoming increasingly prevalent in society. Once deemed
something fit only for degenerates, it has now proliferated via the
internet for anyone to view. This growth in pornographic content
suggests significantly more people are viewing pornography, and viewing
it more often. Cultivation theory offers the viewpoint that as people
consume more of a specific form of media, they tend to believe the norms
and values of that media are reflective of the real world, and so tend
to emulate those beliefs beyond the scope of that media. Consequently,
the most prevalent forms of sexuality presented within porn have
salience for society as a whole, since these formulations are going to
be seen increasingly as what is expected of a sexual relationship.\\
There is currently a gap in the literature on what themes in pornography
are most prevalent, implying that further inquiry needs to be done in
this area, which this present project aims to address. Using an
exhaustive list of all videos posted to the website xHamster between
2007 and 2013, I will examine the prevalence of tags (i.e., video
themes) and their popularity. Ultimately, I am interested in whether or
not there is a relationship between certain tags having increased
popularity over others, and if this popularity varies over time.

\section{Data and Methods}\label{data-and-methods}

Data for this project comes from a publically available dataset on the
website \href{www.sexualitics.org}{sexualitics.org}. The dataset
comprises all videos uploaded to the website ``XHamster'' from the
website's inception in 2007 through February of 2013. This is an
exhaustive dataset with every video uploaded in the timeframe, and
contains 786,122 videos total. The dataset contains variables listing
the video title, date of upload, tag(s) associated with the video,
number of times the video was viewed, number of votes the video has
received, number of comments on the video, how long the video runs in
seconds, and an anonymizied uploader identifier.\\
For the present analysis, the variable containing all of the tags
associated with a video were split into separate boolean categories in
order to obtain a complete list of how many videos were identified with
each tag individually. Tags on XHamster are pre-arranged, meaning
uploaders can choose which tags are associated with their video from a
preset list of possible choices. The dataset used in this sample
included 92 different tags. Many of these tags were organized around
more generalized themes, e.g.~what color someone's hair was, what kind
of breasts an actress has, or what race the performers are. For the
analysis, tags were condensed down to create families of similar tags.
This was done to determine what overarching themes were present, as
analysis over time of 92 separate entities proved too cumbersome, and
most tags were similarly related to others thematically. 11 tag families
were created in total, which incorporated all but 23 of the 92 tags in
the dataset. Most of these tag families comprised between 5 and 10\% of
the total population.\\
\#\#Tag Families \#\#\#Ethnicity and Race XHamster includes tags for
various ethnicities, which were combined into a family to analyze trends
regarding nationality. The ethnicity tags available on XHamster include
Arab, Brazilian, British, Chinese, Czech, Danish, French, German,
Indian, Italian, Japanese, Korean, Russian, Swedish, Thai, and
Turkish.\\
Several tags also existed that encompassed performer's racial category,
including Asian, Black, Latin, and Interracial. In this case,
Interracial was categorized with race due to its relationship to the
race of the performers, but it could potentially have fallen under the
sex act family as well. \#\#\#Body and Appearance Several families were
created for tags that were related to specific body parts or the
appearance of performers. Xhamster lists 3 tags related to hair color,
``Blondes,'' ``Redheads,'' and ``Brunettes.'' These were combined to a
hair family. Similarly, several tags existed to describe women's
breasts: Big Boobs, Nipples, and Tits, which were likewise combined to a
Breasts category. Finally, several tags related to older performers were
combined into an age family; these included MILFS, Grannies, Matures,
and the Old+Young tags. Of note is that two tags, Teens and Babysitters,
referred to younger performers. These were separated out due to the
trends potentially being different between individuals seeking younger
performers versus older ones. Babysitters was then dropped due to
extremely low occurence rates within the population (less than 1,000
total cases). \#\#\#Sex Act The sex act category captures any tag
related to a specific sex act, the idea being that there is a trend in
individuals seeking out specific kinds of sex acts rather than a
particular kind of performer. Sex act tags are comprised of: Anal,
Blowjobs, Bukkake, Cream Pies, Cumshots, Double Penetration, Face
Sitting, Facials, Fingering, Gangbang, Group Sex, Handjobs,
Masturbation, and Threesomes.\\
Several other families of less direct sex acts were also created. A
Fetish family was created to encapsulate niche bodily functions
(Squirting, Gaping), less common body fixations (BBW, Foot Fetish), and
clothing tags (Lingerie, Stockings, Latex). Likewise, tags related to
BDSM were combined into their own family; while Xhamster has a specific
tag for BDSM, I included Spanking, Femdom, and Cuckold into a broader
BDSM tag, as these tags were also related to domination of one sexual
partner by another, or to physical violence during sexual activity.
Finally, Xhamster has numerous tags related to voyeur pornography,
including a voyeur tag, but also tags for Public Nudity, Hidden Cams,
Flashing, Upskirts, and Beach. Beach was included as it is ostensibly
people performing sexual activities in an outdoor, public setting,
despite this potentially including content on private beaches or away
from public view; the theme of it being an open space is still related
to the idea that someone else could be watching the act occur.
\#\#\#Non-Hetero Families Lastly, two tag families were created for
non-heterosexual performers. the gay family was created from the Black
Gays, Gays, and Men tags, notable here is that this includes only tags
related to men, not women. A second tag family was also created for
trans individuals, which is comprised of the Shemale and Ladyboy tags.

\section{Results}\label{results}

\begin{verbatim}
load("../../analysis/output/analyticalData.RData")
tags.super <- c("ethnicity",
                "race",
                "sex.act",
                "fetish",
                "voyeur.super",
                "gay",
                "breasts" 
                )

trends <- NULL
for(tag in tags.super) {
  cat(tag)
  cat("\n")
  temp <- data.frame(year=2007:2013,
                     tag=tag,
                     percent=100*prop.table(table(porn$upload_year, porn[,tag]),1)[,2])
  
  trends <- rbind(trends, temp)
}

ggplot(trends, aes(x=year, y=percent, color=tag, group=tag))+
  geom_point()+
  geom_smooth(se=FALSE)+
  theme_bw()+
  labs(x="Year",
        y="Percent of total videos uploaded",
        title="Major Themes in Pornography Published to XHamster: 2007-2013",
       colour="Theme")

#Second Chart
#Creating master list of tags for analysis
tags.super <- c("hair",
                "bdsm.super",
                "age",
                "trans",
                "Amateur", 
                "Teens", 
                "Hardcore"
)



trends <- NULL
for(tag in tags.super) {
  cat(tag)
  cat("\n")
  temp <- data.frame(year=2007:2013,
                     tag=tag,
                     percent=100*prop.table(table(porn$upload_year, porn[,tag]),1)[,2])
  
  trends <- rbind(trends, temp)
  
}

#Plotting group % by year
ggplot(trends, aes(x=year, y=percent, color=tag, group=tag))+
  geom_point()+
  geom_smooth(se=FALSE)+
  theme_bw()+
  labs(x="Year",
       y="Percent of total videos uploaded",
       title="Major Themes in Pornography Published to XHamster: 2007-2013",
       colour="Theme")
\end{verbatim}

These two charts show the created tag families, as well as the 3 most
popular individual tags that had similar prevalences to the tag
families: Amateur, Teens, and Hardcore. The data was split onto two
charts for readability purposes. By far the most popular tag family was
sex act, with a peak of 40\% of all videos being tagged with a sex act
in 2009. Over time the popularity of this family waned, however it
remains the most popular theme of all families even after this dip in
later years.\\
Gay content has also shown steady, significant increase over the years,
rising from less almost no content to approximately 22\% of all uploaded
materials by 2013. Race likewise has seen an increase over time, as has
fetish content. Some of the more niche content shows steady growth over
time however, as fetish and ethnic content attest.\\
What is perhaps more interesting, however, are the categories that have
declined over time. most notably, Amateur content has experienced a
stark decline, from nearly half of all content uploaded at the site's
inception to approximately 29\% by 2013; the Teens tag shows a nearly
parallel decline as well. Hardcore content has also declined
significantly over time, as has content focused on breasts.

\section{Conclusions}\label{conclusions}



\renewcommand\refname{References}
\bibliography{../project.bib}
\end{document}
